# A Minimal Example for Markdown

This is a minimal example of using **knitr** to produce an _HTML_ page from _Markdown_.

## R code chunks

```{r setup}
# set global chunk options: images will be 7x5 inches
opts_chunk$set(fig.width=7, fig.height=5)
```

Now we ^write^ some code chunks in this markdown file:

```{r computing}
x <- 1+1 # a simple calculator
set.seed(123)
rnorm(5)  # boring random numbers
```

We can also produce plots:

```{r graphics}
par(mar = c(4, 4, .1, .1))
with(mtcars, {
  plot(mpg~hp, pch=20, col='darkgray')
  lines(lowess(hp, mpg))
})
```

Or integrate with LabKey:

```{r echo=FALSE}
#
# setup: load data
#
print('Setup script time');
ptm <- proc.time();
if (!exists("sharedSession")) {
    print('running setup code ...');
    print('scriptpad module unavailable. Defining data frame manually.');
    participantid <- c(249318596, 249318596, 249318596, 249318596, 249318596, 249318596, 249318596, 249318596, 249318596, 249318596, 249320107, 249320107, 249320107, 249320107, 249320107, 249320127, 249320127, 249320127, 249320127, 249320127, 249320127, 249320127, 249320489, 249320489, 249320489, 249320489, 249320489, 249320897, 249320897, 249320897, 249320897, 249320897, 249320897, 249325717, 249325717, 249325717, 249325717, 249325717);
    weight_kg <- c(86, 84, 83, 80, 79, 79, 79, 78, 77, 75, 55, 54, 52, 50, 51, 62, 64, 63, 65, 65, 67, 69, 90, 86, 84, 75, 72, 73, 77, 74, 75, 77, 75, 98, 111, 110, 112, 138);
    temp_c <- c(36.0, 37.0, 37.0, 36.7, 36.8, 37.3, 38.0, 40.0, 39.0, 39.0, 37.0, 37.0, 36.9, 37.3, 36.6, 36.9, 37.3, 36.6, 39.9, 36.0, 41.0, 38.0, 36.9, 40.0, 37.2, 36.5, 37.5, 37.5, 36.8, 37.0, 36.0, 37.2, 36.7, 37.4, 38.0, 33.0, 37.0, 36.5);
    systolicbloodpressure <- c(129, 133, 133, 135, 142, 129, 122, 122, 121, 123, 120, 123, 120, 139, 114, 140, 179, 134, 135, 131, 137, 129, 124, 134, 128, 140, 130, 112, 121, 120, 134, 115, 97, 108, 137, 136, 133, 156);
    diastolicbloodpressure <- c(76, 79, 85, 85, 90, 87, 80, 76, 78, 76, 85, 86, 83, 80, 79, 90, 110, 89, 89, 74, 87, 76, 75, 75, 78, 90, 90, 74, 79, 72, 85, 70, 67, 74, 90, 112, 74, 117);
    pulse <- c(64, 67, 68, 70, 75, 79, 64, 63, 65, 64, 63, 65, 62, 66, 64, 70, 74, 75, 76, 59, 65, 76, 70, 70, 56, 78, 70, 67, 65, 66, 69, 67, 70, 89, 77, 112, 90, 113);
    labkey.data <- data.frame(participantid, weight_kg, temp_c, systolicbloodpressure, diastolicbloodpressure, pulse);
    sharedSession <- 1;
}
print(proc.time() - ptm);
```


```{r blood-pressure-scatter, message=FALSE, warning=FALSE, echo=FALSE, fig.align='center'}
#
# plot 1
#
plot(labkey.data$diastolicbloodpressure, labkey.data$systolicbloodpressure,
main="Diastolic vs. Systolic Pressures: All Visitsx",
ylab="Systolic (mm Hg)", xlab="Diastolic (mm Hg)", ylim =c(60, 200));
abline(lsfit(labkey.data$diastolicbloodpressure, labkey.data$systolicbloodpressure));

#
# plot 2
#
data_means <- aggregate(labkey.data, list(ParticipantID =
 labkey.data$participantid), mean, na.rm = TRUE);

op <- par(mfcol = c(2, 2)) # 2 x 2 pictures on one plot
c11 <- plot(data_means$diastolicbloodpressure, data_means$weight_kg, ,
 xlab="Diastolic Blood Pressure (mm Hg)", ylab="Weight (kg)",
 mfg=c(1, 1))
abline(lsfit(data_means$diastolicbloodpressure, data_means$weight_kg))
c21 <- plot(data_means$diastolicbloodpressure, data_means$systolicbloodpressure, ,
 xlab="Diastolic Blood Pressure (mm Hg)",
 ylab="Systolic Blood Pressure (mm Hg)", mfg= c(2, 1))
abline(lsfit(data_means$diastolicbloodpressure, data_means$systolicbloodpressure))
c21 <- plot(data_means$diastolicbloodpressure, data_means$pulse, ,
 xlab="Diastolic Blood Pressure (mm Hg)",
 ylab="Pulse Rate (Beats/Minute)", mfg= c(1, 2))
abline(lsfit(data_means$diastolicbloodpressure, data_means$pulse))
c21 <- plot(data_means$diastolicbloodpressure, data_means$temp_c, ,
 xlab="Diastolic Blood Pressure (mm Hg)",
 ylab="Temperature (Degrees C)", mfg= c(2, 2))
abline(lsfit(data_means$diastolicbloodpressure, data_means$temp_c))
par(op); #Restore graphics parameters
```


## Inline code

Inline R code is also supported, e.g. the value of `x` is `r x`, and 2 x pi = `r round(2*pi, 3)`.

## Math

LaTeX math as usual: $f(\alpha, \beta) \propto x^{\alpha-1}(1-x)^{\beta-1}$.

## Misc

You can indent code chunks so they can nest within other environments such as lists.

1. the area of a circle with radius x
    ```{r foo}
    pi * x^2
    ```
2. OK, that is great

To compile me, use

```{r compile, eval=FALSE}
library(knitr)
knit('knitr-minimal.Rmd')
```

## Conclusion

Markdown is super easy to write. Go to **knitr** [homepage](http://yihui.name/knitr) for details.